\begin{thebibliography}{9}

\bibitem{yanai}
柳井啓司: 一般物体認識の現状と今後,
情報処理学会論文誌. コンピュータビジョンとイメージメディア, Vol.48, No.16, pp. 1-24 (2007).

\bibitem{mori}
森靖英, 高橋裕信, 岡隆一: 単語群付き画像の分割クラスタリングによる未知画像からの関連単語推定, 
電子情報通信学会論文誌, Vol.J84-D-II, No.4, pp.649-658 (2001).

\bibitem{imagenet}
J. Deng, W. Dong, R. Socher, L.-J. Li, K. Li, and L. Fei-Fei: 
ImageNet: A large-scale hierarchical image database, 
{\it Proceedings of IEEE Conference on Computer Vision and Pattern Recognition}, pp. 248-255 (2009).

\bibitem{torralba}
A. Torralba, R. Fergus, and W. Freeman:
80 million tiny images: A large data set for nonparametric object and scene recognition, 
{\it IEEE Transactions on Pattern Analysis and Machine Intelligence}, Vol.30, pp. 1958-1970 (2008).

% PAMI, 30(11):1958–1970, November 2008.

\bibitem{duygulu}
Duygulu, P., Barnard, K., de Freitas, N., and Forsyth, D.: 
Object recognition as machine translation: Learning a lexicon for a fixed image vocabulary, 
{\it Proceedings of the 7th European Conference on Computer Vision-Part IV}, pp. 97-112 (2002).

\bibitem{jeon}
Jeon, J., Lavrenko, V. and Manmatha, R.: 
Automatic Image Annotation and Retrieval using Cross-media Relevance Models, 
{\it Proceedings of the 26th annual international ACM SIGIR conference on Research and development in informaion retrieval}, 
pp. 119--126 (2003).

\bibitem{watanabe}
渡邉裕樹, 秋良直人, 廣池敦, 松原大輔, 平松義崇, 永吉洋登, 影広達彦, 久光徹 : 
大規模Web画像データベースを用いた画像アノテーションシステムの構築, 情報処理学会研究報告, Vol.2012-CVIM-181, No.8, pp. 1-8 (2012)

\end{thebibliography}